---
title: "project_rmd"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = TRUE)
```

# Important Readings

ISLR v2

Chapter 05 - Resampling Methods (to handle small n)

Chapter 06 - Linear Model Selection and Regularization (to handle large dimension)

Chapter 08 - Tree-Based Methods

Chapter 09 - SVM

Chapter 10 - Deep Learning (CNN & RNN)

# Import Libraries and Read Files

```{r, message = F, warning = F}
library('readxl')
library('ggplot2')
library('GGally')
```

```{r}
filename <- 'Dataset/WBA_Final_Merged_Absorbance-Admittance-Phase-CMG_Reduced-Cleaned.xlsx'

raw.absorbance <- read_excel(filename, sheet = 1)
raw.admittance <- read_excel(filename, sheet = 2)
raw.phase <- read_excel(filename, sheet = 3)
```

# Data Preprocessing

### Separating Data into Frequency and Core

```{r}
freq.regex <- 'f[(]'
freq.columns <- grep(freq.regex, names(raw.phase))

# Extract Frequencies
freq.admittance <- raw.admittance[ , freq.columns ]
freq.phase <- raw.phase[ , freq.columns ]
# absorbance has 2 less columns
freq.absorbance <- raw.absorbance[ , freq.columns - 2 ] 

# Extract Core Patient Information
core.info <- raw.phase[ , -freq.columns ]
```

### Remove Columns

```{r}
unused.columns <- c(
  # One Value Columns
  'PTA0.5', # 20
  'PTA1', # 20
  'PTA2', # 20
  'PTA4', # 20
  'PTAAv4FA', # 20
  'PTAAv4FAPoF', # P
  'PTAAv4FAPoFC', # 0
  
  # Redundant Columns
  'AgeY', # there's age in month AgeM
  'DOT', 'DOB', # AgeM = DOT - DOB
  'TympType', # derived from ECV, TPP, SC
  # 'TympPoF', # derived from TympType
  # 'OAEPoF', # derived from OAE1, OAE1.4, OAE2, OAE2.8, OAE4
  
  # Code Columns
  'OAEPoFC', # OAEPoF
  'Ear coded', # EarSide
  
  # NA Columns
  'Unnamed: 49',
  'Unnamed: 55',
  'Unnamed: 64',
  
  # I think we don't need these
  'Subject', 
  'School', 
  'SchoolCode',
  
  'Eth1',
  'Eth2',
  'Unnamed: 15',
  'Lang1',
  'Lang2',
  'Lang3',
  'Unnamed: 19',
  'Pressure'
)

core.info <- core.info[ , !(names(core.info) %in% unused.columns) ]
```

### Clean NA Cells

```{r}
core.info$TPP[ is.na(core.info$TPP) ] <- median(core.info$TPP, na.rm = TRUE)
core.info$SC[ is.na(core.info$SC) ] <- median(core.info$SC, na.rm = TRUE)
```

### Change negative values

### Export to PDF HERE

# Initial Inspections

### Inspect Response Variable

We got an imbalanced dataset.

```{r}
target <- 'OverallPoF'
barplot(table(core.info[ target ]), col = c('red3', 'green3'))
```

### Frequency Predictor Variables

```{r}
boxplot(freq.absorbance)
```

```{r}
boxplot(freq.admittance)
```

```{r}
boxplot(freq.phase)
```

### Other Predictor Variables

```{r}
str(core.info)
```

```{r}
ggplot(core.info, aes(as.factor(`Unnamed: 15`), ..count..)) + 
  geom_bar(aes(fill = OverallPoF), position = 'dodge')
```

```{r}
OAE.ggp <- ggpairs(columns = 13 : 17, data = core.info)
print(OAE.ggp, progress = F)
```

```{r}
ggplot(core.info, aes(EarSide, ..count..)) + 
  geom_bar(aes(fill = OverallPoF), position = 'dodge')
```

```{r}
for (col in names(core.info)) {
  
  if (class(core.info[[ col ]]) != 'numeric') next
  hist(core.info[[ col ]], main = col)
}
```
